A Hierarchical Bayesian Framework for Exoplanetary Stellar Obliquity Distribution

### 2023-02-08 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure}[ht!]
    \script{simulation.py}
    \includegraphics[width=\linewidth]{figures/simulation.pdf}
    \caption{Inferred stellar obliquity distributions from sky-projected stellar obliquities with or without stellar inclination measurements. Each row presents a set of simulated data where the underlying $\cos{\psi}$ distribution is known and shown as grey dashed curves. The inferred $\cos{\psi}$ distributions with or without stellar inclination measurements are shown in orange and blue curves, respectively. The shallow contours are 1-$\sigma$ and 2-$\sigma$ uncertainties of the inferred distributions.}
    \label{fig:simulation}
\end{figure}

@@

\begin{figure}[ht!]
    \script{psi_dist.py}
    \begin{centering}
        \includegraphics{figures/psi_dist.pdf}
        \caption{Stellar obliquity distribution of all exoplanetary systems with sky-projected stellar obliquity measurements. The inference is purely from observed sky-projected stellar obliquities and assumes the stellar inclination is isotropic.}
        \label{fig:psi_dist}
    \end{centering}
\end{figure}

>>>>

% \begin{figure}[ht!]
%     \script{simulation.py}
%     \includegraphics[width=\linewidth]{figures/simulation.pdf}
%     \caption{Inferred stellar obliquity distributions from sky-projected stellar obliquities with or without stellar inclination measurements. Each row presents a set of simulated data where the underlying $\cos{\psi}$ distribution is known and shown as grey dashed curves. The inferred $\cos{\psi}$ distributions with or without stellar inclination measurements are shown in orange and blue curves, respectively. The shallow contours are 1-$\sigma$ and 2-$\sigma$ uncertainties of the inferred distributions.}
%     \label{fig:simulation}
% \end{figure}

@@

\begin{figure}[ht!]
    \script{psi_plot.py}
    \begin{centering}
        \includegraphics{figures/psi_dist.pdf}
        \caption{Stellar obliquity distribution of all exoplanetary systems with sky-projected stellar obliquity measurements. The inference is purely from observed sky-projected stellar obliquities and assumes the stellar inclination is isotropic.}
        \label{fig:psi_dist}
    \end{centering}
\end{figure}
